Race results from the twelfth edition of the

### 2025-02-27 inst/cheering.Rmd

In the following, I use the ''race'' metaphor: five runners take part
in a race and arrive in order: $a\succ b\succ c\succ d\succ 5e.
Consider the following Plackett-Luce likelihood function for this
observation:

@@

```{r,defineredbuslf}
`RB_BB_LF` <- function(s){
    ec <- c(C=1,T=2,RB=3,BB=3,W=4) # equivalence classes
    h <- c(1,1,s,1)                # strength of support
    (
        cheering3(v=c("RB","BB","C" ,"T","W"),e=ec,h=h)*3 +
        cheering3(v=c("BB","RB","T" ,"C","W"),e=ec,h=h)*2 +
        cheering3(v=c("T" ,"BB","RB","C","W"),e=ec,h=h)*2 +
        cheering3(v=c("W" ,"BB","RB","T","C"),e=ec,h=h)*4 +
        cheering3(v=c("C" ,"RB","BB","W","T"),e=ec,h=h)*4 +
        cheering3(v=c("BB","C" ,"RB","T","W"),e=ec,h=h)*3
    )
}
```

@@

```{r,label=proflikeredbus,cache=TRUE}
o <- function(s){maxp(RB_BB_LF(s),give=TRUE,n=1)$likes} # optimand
s <- exp(seq(from=log(1.3),to=log(47),len=17)) # putative similarity measures
L <- sapply(s,o)
L <- L-max(L)
```

@@

a <- a[a$university_name %in% wanted,]
a <- cbind(a,"top7rank"=0)
for(y in unique(a$year)){
    a[a$year==y,"top7rank"] <- order(
     			  as.numeric(a[a$year==y,"world_rank"]) +
                                     a[a$year==y,"research"]/1e6,
decreasing=TRUE)}
a <- a[,c("top7rank","university_name","year")]
a <- reshape(a,idvar="university_name",timevar="year",direction="wide")
for(i in seq_len(nrow(a))){
   a$university_name[i] <- names(which(wanted == a$university_name[i]))
}
rownames(a) <- a$university_name
a <- a[,-1]
colnames(a) <- paste("Y",2011:2016,sep="")
a
H <- ordertable2supp(a)
```

>>>>

In the following, I use the ''race'' metaphor: five runners take part
in a race and arrive in order: $a\succ b\succ c\succ d\succ e$.
Consider the following Plackett-Luce likelihood function for this
observation:

@@

```{r,defineredbuslf}
`RB_BB_LF` <- function(s){
    ec <- c(C=1,T=2,RB=3,BB=3,W=4) # equivalence classes
    h <- c(1,1,s,1)                # strength of support
    (
        cheering3(v=c("RB","BB","C" ,"T","W"), e=ec, h=h)*3 +
        cheering3(v=c("W" ,"BB","RB","C","T"), e=ec, h=h)*7 +
        cheering3(v=c("W" ,"RB","BB","C","T"), e=ec, h=h)*8 +
        cheering3(v=c("W" ,"BB","RB","T","C"), e=ec, h=h)*7 +
        cheering3(v=c("W" ,"RB","BB","C","T"), e=ec, h=h)*7 +
        cheering3(v=c("RB","BB","C" ,"T","W"), e=ec, h=h)*3 +
        cheering3(v=c("RB","BB","C" ,"T","W"), e=ec, h=h)*3 +
        cheering3(v=c("BB","RB","T" ,"C","W"), e=ec, h=h)*2 +
        cheering3(v=c("T" ,"BB","RB","C","W"), e=ec, h=h)*2 +
        cheering3(v=c("W" ,"BB","RB","T","C"), e=ec, h=h)*4 +
        cheering3(v=c("C" ,"RB","BB","W","T"), e=ec, h=h)*4 +
        cheering3(v=c("BB","C" ,"RB","T","W"), e=ec, h=h)*3
    )
}
```

@@

```{r,label=proflikeredbusbluebus,cache=TRUE}
o <- function(s){maxp(RB_BB_LF(s),give=TRUE,n=1)$likes} # optimand
s <- exp(seq(from=log(1.3),to=log(147),len=17)) # putative similarity measures
L <- sapply(s,o)
L <- L-max(L)
```

@@

a <- a[a$university_name %in% wanted,]
a <- cbind(a,"top7rank"=0)
for(y in unique(a$year)){
    a[a$year==y,"top7rank"] <- order(
     			  as.numeric(a[a$year==y,"world_rank"]) +
                                     a[a$year==y,"research"]/1e6,
decreasing=TRUE)}
a <- a[,c("top7rank","university_name","year")]
a <- reshape(a,idvar="university_name",timevar="year",direction="wide")
for(i in seq_len(nrow(a))){
   a$university_name[i] <- names(which(wanted == a$university_name[i]))
}
rownames(a) <- a$university_name
a <- a[,-1]
colnames(a) <- paste("Y",2011:2016,sep="")
a
H <- suppfun(ordertable(a))
```

### 2025-02-27 inst/counterstrike.Rmd

    d <- strsplit(a$deathorder[i],", ")[[1]]
    H3 <- H3 + cheering3(d, e=ec, help=c(1,lam))
  }
  return(H3)
}

@@

>>>>

    d <- strsplit(a$deathorder[i],", ")[[1]]
    H3 <- H3 + cheering3(d, e=ec, help=c(1,lam))
  }
  return(H3)
}
```

  Now some profile likelihood

@@

```{r calcklikef, cache=TRUE}
f <- function(l){maxp(mk(l), give=1)$`Log-likelihood`}
lam <- seq(from = 0.01,to = 1.1, len = 43)
L <- sapply(lam, f)
```

```{r plotlikelam}
plot(lam, L - max(L), type='b')
plot(log(lam), L - max(L), type='b')
```

```{r findaopt, cache=TRUE}
optlam <- optimize(f,c(0.09, 0.14), maximum = TRUE)
```

```{r showoptlam}
optlam
```

```{r}
maxp(mk(optlam$maximum))
```

### 2025-02-27 inst/pentathlon.Rmd
S3 classes ordertable and ranktable

```{r readpentathlontable}
pentathlon_table <- as.matrix(read.table("pentathlon.txt"))
pentathlon_table
```

@@

```{r showpiechart,cache=TRUE}
pentathlon <- ordertable2supp(pentathlon_table)
pentathlon_maxp <- maxp(pentathlon)
pentathlon_maxp
pie(pentathlon_maxp)
```

>>>>

```{r readpentathlontable}
pentathlon_table <- ordertable(as.matrix(read.table("pentathlon.txt")))
pentathlon_table
```

@@

```{r showpiechart,cache=TRUE}
pentathlon <- suppfun(pentathlon_table)
pentathlon_maxp <- maxp(pentathlon)
pentathlon_maxp
pie(pentathlon_maxp)
```

### 2025-02-27 inst/salad.Rmd

```{r}
rownames(salad) <-
   paste("j",formatC(seq_len(nrow(salad)),width=2,format="d",flag="0"),sep="")
ts <- t(salad)
ts
```

@@

```{r useslickmethod,cache=TRUE}
(H2 <- ordertable2supp(ts))
```

>>>>

```{r}
rownames(salad) <-
   paste("j",formatC(seq_len(nrow(salad)),width=2,format="d",flag="0"),sep="")
ts <- ordertable(t(salad))
```

@@

```{r useslickmethod,cache=TRUE}
(H2 <- suppfun(ts))
```

### 2025-02-27 inst/volvo.Rmd

```{r readvolvotable}
volvo_table <- read.table("volvo.txt")
volvo_table
```

@@

```{r specifynoscore,cache=TRUE}
volvo <- ordertable2supp(volvo_table,noscore=c("DNF","DNS"))
(volvo_maxp <- maxp(volvo))
```

@@

```{r,label=savecurlingdataset}
save(volvo_table,volvo_maxp,volvo,file="volvo.rda")
```

>>>>

```{r readvolvotable}
volvo_table <- ordertable(read.table("volvo.txt"))
volvo_table
```

@@

```{r specifynoscore,cache=TRUE}
volvo <- suppfun(volvo_table, noscore=c("DNF", "DNS"))
(volvo_maxp <- maxp(volvo))
```

@@

```{r,label=savecurlingdataset}
save(volvo_table, volvo_maxp, volvo, file = "volvo.rda")
```
